Spatial distribution of environmental DNA in a nearshore marine habitat

### 2017-01-07 Manuscript/v1.1_PeerJ/carkeek_grid.tex
add paragraph on marker choice to discussion

The marker we chose for this study detects a wide variety of metazoans while excluding other more common taxa; however, it does not effectively discriminate among species within a higher group in all cases. Other markers, such as mitochondrial cytochrome c oxidase subunit 1 (COX1, CO1, or COI) provide adequate species-level resolution in some metazoan groups, but have other shortcomings including taxon dropout (Deagle2014) and amplification of more abundant non-metazoans, as we discovered in an accompanying study (Kelly2016FMS). Both have undesirable effects of biasing estimates of diversity: in our case, it is possible that the lumping of multiple species into one group underestimates the true richness of the group and of the entire sample. In turn, this could obscure true underlying patterns of diversity. In the case of COX1, well-documented primer biases cause failure to amplify some taxa, particularly in mixed samples, with the same result. In fact, even surveys relying on traditional capture techniques (e.g. seine nets) and morphological characteristics are subject to biases imposed by the sampling gear (e.g. mesh size), the observer (e.g. taxonomic expertise), and organisms (e.g. morphologically cryptic species). Until whole-genome sequencing of individual cells is a reality, the tradeoffs between taxonomic breadth and resolution will continue to be problematic for metabarcoding studies, just as they are for more traditional ecological survey methods (Kelly2016FMS).

>>>>

The marker we chose for this study detects a wide variety of metazoans while excluding other more common taxa; however, it does not effectively discriminate among species within a higher group in all cases. Other markers, such as mitochondrial cytochrome c oxidase subunit 1 (COX1, CO1, or COI) provide adequate species-level resolution in some metazoan groups, but have other shortcomings including taxon dropout \citep{Deagle2014} and amplification of more abundant non-metazoans, as we discovered in an accompanying study \citep{Kelly2016FMS}. Both have undesirable effects of biasing estimates of diversity: in our case, it is possible that the lumping of multiple species into one group underestimates the true richness of the group and of the entire sample. In turn, this could obscure true underlying patterns of diversity. In the case of COX1, well-documented primer biases cause failure to amplify some taxa, particularly in mixed samples, with the same result. In fact, even surveys relying on traditional capture techniques (e.g. seine nets) and morphological characteristics are subject to biases imposed by the sampling gear (e.g. mesh size), the observer (e.g. taxonomic expertise), and organisms (e.g. morphologically cryptic species). Until whole-genome sequencing of individual cells is a reality, the tradeoffs between taxonomic breadth and resolution will continue to be problematic for metabarcoding studies, just as they are for more traditional ecological survey methods \citep{Kelly2016FMS}.
